---
output: html_document
---

> 8. In the lab, a classification tree was applied to the Carseats data set after
converting Sales into a qualitative response variable. Now we will
seek to predict Sales using regression trees and related approaches,
treating the response as a quantitative variable.  
(a) Split the data set into a training set and a test set.  
(b) Fit a regression tree to the training set. Plot the tree, and interpret
the results. What test MSE do you obtain?  
(c) Use cross-validation in order to determine the optimal level of
tree complexity. Does pruning the tree improve the test MSE?  
(d) Use the bagging approach in order to analyze this data. What
test MSE do you obtain? Use the importance() function to determine
which variables are most important.  
(e) Use random forests to analyze this data. What test MSE do you
obtain? Use the importance() function to determine which variables
are most important. Describe the effect of m, the number of
variables considered at each split, on the error rate
obtained.  

```{r 8.8}
library(ISLR)
attach(Carseats)

# (a)
set.seed(0)
record_num = nrow(Carseats)
test_percent = 1/10
train_idx = sample(record_num, record_num*(1-test_percent))
train_data = Carseats[train_idx,]
test_data = Carseats[-train_idx,]

# (b)
#install.packages('tree')
library(tree)
treer_model = tree(Sales ~ ., data = train_data)
summary(treer_model)
# plot tree
plot(treer_model)
text(treer_model)
# mse
pred.treer = predict(treer_model,test_data)
mse = mean((pred.treer-test_data$Sales)^2)
print(mse) # 7.747241

# (c)
cv.treer_model = cv.tree(treer_model,K = 10)
par(mfrow = c(1, 2))
plot(cv.treer_model$size,cv.treer_model$dev,type = 'b')
# k	cost-complexity parameter defining either a specific subtree of tree (k a scalar) or the (optional) sequence of subtrees minimizing the cost-complexity measure (k a vector). If missing, k is determined algorithmically.
plot(cv.treer_model$k,cv.treer_model$dev,type = 'b')
# size = 9
pruned.treer = prune.tree(treer_model, best = 9)
# plot
par(mfrow = c(1, 1))
plot(pruned.treer)
text(pruned.treer)
# mse
pred.pruned.treer = predict(pruned.treer,test_data)
mse = mean((pred.pruned.treer-test_data$Sales)^2)
print(mse) # 7.62105

# (d)
#install.packages('randomForest')
library(randomForest)
set.seed(0)
# bag is a special case of randomforest that m=p
bag.model = randomForest(Sales ~ ., data = train_data,mtry = ncol(Carseats) - 1, importance = T)
pred.bag= predict(bag.model, test_data)
mse = mean((pred.bag-test_data$Sales)^2)
print(mse) 

# important variables: ShelveLoc > Price > CompPrice > Advertising > Age > ...
importance(bag.model)

# (e) use m = p/2 randomforest, which has a little larger mse than bagging 
rf.model = randomForest(Sales ~ ., data = train_data, mtry = floor(ncol(Carseats)/2), importance = T)
pred.rf= predict(rf.model, test_data)
mse = mean((pred.rf-test_data$Sales)^2)
print(mse) 

# important variables:  Price > ShelveLoc > CompPrice > Advertising > Age > ...  
importance(rf.model)
```


> 10.  We now use boosting to predict Salary in the Hitters data set.  
(a) Remove the observations for whom the salary information is
unknown, and then log-transform the salaries.  
(b) Create a training set consisting of the first 200 observations, and
a test set consisting of the remaining observations.  
(c) Perform boosting on the training set with 1,000 trees for a range
of values of the shrinkage parameter λ. Produce a plot with
different shrinkage values on the x-axis and the corresponding
training set MSE on the y-axis.  
(d) Produce a plot with different shrinkage values on the x-axis and
the corresponding test set MSE on the y-axis.  
(e) Compare the test MSE of boosting to the test MSE that results
from applying two of the regression approaches seen in
Chapters 3 and 6.  
(f) Which variables appear to be the most important predictors in
the boosted model?  
(g) Now apply bagging to the training set. What is the test set MSE
for this approach?  

```{r 8.10}
# (a)
library(ISLR)
Hitters = Hitters[-which(is.na(Hitters$Salary)), ]
Hitters$Salary = log(Hitters$Salary)

# (b)
train = 1:200
Hitters.train = Hitters[train, ]
Hitters.test = Hitters[-train, ]

# (c) (d)
# install.package('gbm')
library(gbm)
set.seed(0)
# init
pows = seq(-10, -0.2, by = 0.1)
lambdas = 10^pows
length.lambdas = length(lambdas)
train.errors = rep(NA, length.lambdas)
test.errors = rep(NA, length.lambdas)
# start
for (i in 1:length.lambdas) {
    boost.hitters = gbm(Salary ~ ., data = Hitters.train, distribution = "gaussian", 
        n.trees = 1000, shrinkage = lambdas[i])
    train.pred = predict(boost.hitters, Hitters.train, n.trees = 1000)
    test.pred = predict(boost.hitters, Hitters.test, n.trees = 1000)
    train.errors[i] = mean((Hitters.train$Salary - train.pred)^2)
    test.errors[i] = mean((Hitters.test$Salary - test.pred)^2)
}

plot(lambdas, train.errors, type = "b")
plot(lambdas, test.errors, type = "b",col='red')

# (e)
# linear regression
lm.fit = lm(Salary ~ ., data = Hitters.train)
lm.pred = predict(lm.fit, Hitters.test)
mean((Hitters.test$Salary - lm.pred)^2)

# lasso
library(glmnet)
set.seed(0)
x = model.matrix(Salary ~ ., data = Hitters.train)
y = Hitters.train$Salary
x.test = model.matrix(Salary ~ ., data = Hitters.test)
lasso.fit = glmnet(x, y, alpha = 1)
lasso.pred = predict(lasso.fit, s = 0.01, newx = x.test)
mean((Hitters.test$Salary - lasso.pred)^2)

# (f) CAtBat > PutOuts > CWalks > Walks > CRuns > Years   
boost.best = gbm(Salary ~ ., data = Hitters.train, distribution = "gaussian",n.trees = 1000, shrinkage = lambdas[which.min(test.errors)])
summary(boost.best)

# (g)
bag.hitters = randomForest(Salary ~ ., data = Hitters.train, ntree = 500, mtry = ncol(Hitters)-1)
bag.pred = predict(bag.hitters, Hitters.test)
mean((Hitters.test$Salary - bag.pred)^2)
```


> 12. Apply boosting, bagging, and random forests to a data set of your
choice. Be sure to fit the models on a training set and to evaluate their
performance on a test set. How accurate are the results compared
to simple methods like linear or logistic regression? Which of these
approaches yields the best performance?

```{r 8.12}
library(MASS)
attach(Boston)
test_percent = 1/10
train_idx = sample(record_num, record_num*(1-test_percent))
train_data = Boston[train_idx,]
test_data = Boston[-train_idx,]
### linear(41.3),boosting(22.0),bagging(17.1*best),randomforest(18.2)
# linear regression
lm.fit = lm(medv ~ . , data = train_data)
lm.pred = predict(lm.fit, newdata = test_data)
print(mean((lm.pred - test_data$medv)^2))

# boosting
library(gbm)
boost.model=gbm(medv~.,data=train_data,distribution="gaussian",n.trees=5000,interaction.depth=4)
pred.boost = predict(boost.model,newdata=test_data,n.trees=5000)
print(mean((pred.boost-test_data$medv)^2)) 

# bagging
library(randomForest)
set.seed(0)
bag.model = randomForest(medv ~ ., data = train_data,mtry = ncol(Carseats) - 1, importance = T)
pred.bag= predict(bag.model, test_data)
print(mean((pred.bag-test_data$medv)^2)) 

# randomforest
rf.model = randomForest(medv ~ ., data = train_data, mtry = floor(ncol(Carseats)/2), importance = T)
pred.rf= predict(rf.model, test_data)
print(mean((pred.rf-test_data$medv)^2))
```
