---
title: "SL homework 14"
author: "zhixue"
date: "2019年6月4日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 10.7 exercises
2. Suppose that we have four observations, for which we compute a
dissimilarity matrix, given by
$$\begin{bmatrix}
 & 0.3 & 0.4 & 0.7\\ 
0.3 &  & 0.5 & 0.8\\ 
0.4 & 0.5 &  & 0.45\\ 
0.7 & 0.8 & 0.45 & 
\end{bmatrix}.$$
For instance, the dissimilarity between the first and second observations
is 0.3, and the dissimilarity between the second and fourth
observations is 0.8.  
(a) On the basis of this dissimilarity matrix, sketch the dendrogram
that results from hierarchically clustering these four observations
using complete linkage. Be sure to indicate on the plot the
height at which each fusion occurs, as well as the observations
corresponding to each leaf in the dendrogram.  
(b) Repeat (a), this time using single linkage clustering.  
(c) Suppose that we cut the dendogram obtained in (a) such that
two clusters result. Which observations are in each cluster?  
(d) Suppose that we cut the dendogram obtained in (b) such that
two clusters result. Which observations are in each cluster?  
(e) It is mentioned in the chapter that at each fusion in the dendrogram,
the position of the two clusters being fused can be
swapped without changing the meaning of the dendrogram. Draw
a dendrogram that is equivalent to the dendrogram in (a), for
which two or more of the leaves are repositioned, but for which
the meaning of the dendrogram is the same.

```{r 10.2}
#a
d = as.dist(matrix(c(0, 0.3, 0.4, 0.7, 
                     0.3, 0, 0.5, 0.8,
                     0.4, 0.5, 0.0, 0.45,
                     0.7, 0.8, 0.45, 0.0), nrow=4))
plot(hclust(d, method="complete"))
#b
plot(hclust(d, method="single"))
#c {1,2}, {3,4}
#d {4}, {1,2,3}
#e
plot(hclust(d, method="complete"), labels=c(2,1,4,3))
```



4. Suppose that for a particular data set, we perform hierarchical clustering
using single linkage and using complete linkage. We obtain two
dendrograms.  
(a) At a certain point on the single linkage dendrogram, the clusters
{1, 2, 3} and {4, 5} fuse. On the complete linkage dendrogram,
the clusters {1, 2, 3} and {4, 5} also fuse at a certain point.
Which fusion will occur higher on the tree, or will they fuse at
the same height, or is there not enough information to tell?  
(b) At a certain point on the single linkage dendrogram, the clusters
{5} and {6} fuse. On the complete linkage dendrogram, the clusters
{5} and {6} also fuse at a certain point. Which fusion will
occur higher on the tree, or will they fuse at the same height, or
is there not enough information to tell?

#### Answer
a. There not enough information to tell. If the max(complete) dissimilarity is equal to the min(single) dissimilarity, they fuse at the same height, otherwise the min(single) would fuse early.  
b. They fuse at the same height because the dissimilarity between 5 and 6 is only decided by two points. IN other words, the max dissimilarity is equal to the min dissimilarity.




6. A researcher collects expression measurements for 1,000 genes in 100
tissue samples. The data can be written as a 1, 000 × 100 matrix,
which we call X, in which each row represents a gene and each column
a tissue sample. Each tissue sample was processed on a different
day, and the columns of X are ordered so that the samples that were
processed earliest are on the left, and the samples that were processed
later are on the right. The tissue samples belong to two groups: control(C) and treatment (T). The C and T samples were processed
in a random order across the days. The researcher wishes to determine
whether each gene’s expression measurements differ between the
treatment and control groups.
As a pre-analysis (before comparing T versus C), the researcher performs
a principal component analysis of the data, and finds that the
first principal component (a vector of length 100) has a strong linear
trend from left to right, and explains 10 % of the variation. The researcher
now remembers that each patient sample was run on one of
two machines, A and B, and machine A was used more often in the
earlier times while B was used more often later. The researcher has
a record of which sample was run on which machine.  
(a) Explain what it means that the first principal component “explains
10 % of the variation”.  
(b) The researcher decides to replace the (j, i)th element of X with
$$x_{ji}-\phi_{j1}z{i1}$$
where $z_{i1}$ is the ith score, and $φ_{j1}$ is the jth loading, for the first
principal component. He will then perform a two-sample t-test
on each gene in this new data set in order to determine whether
its expression differs between the two conditions. Critique this
idea, and suggest a better approach. (The principal component
analysis is performed on $X^T$ ).  
(c) Design and run a small simulation experiment to demonstrate
the superiority of your idea.  

a. Only 10% variation is catched by first principal component(a linear combine of genes) while left 90% varation is lost.

b. It is better to deal with batch effects(produced by different machine A or B) before using two-sample test.

c. Doing simulation of batch effects, if batch effects are included, the proportion of variance will be larger.
```{r 10.6}
#generate
set.seed(0)
control = matrix(rnorm(50*1000),ncol=50)
treatment = matrix(rnorm(50*1000),ncol=50)
express = cbind(control,treatment)
express[1,] = seq(-50,49)

pr.out = prcomp(scale(express))
summary(pr.out)$importance[,1]

#add batch effect
new_express = rbind(express,c(rep(34,50),rep(1,50)))
pr.out = prcomp(scale(new_express))
summary(pr.out)$importance[,1]
```


8. In Section 10.2.3, a formula for calculating PVE was given in Equation
10.8. We also saw that the PVE can be obtained using the sdev
output of the prcomp() function.
On the USArrests data, calculate PVE in two ways:
(a) Using the sdev output of the prcomp() function, as was done in
Section 10.2.3.
(b) By applying Equation 10.8 directly. That is, use the prcomp()
function to compute the principal component loadings. Then,
use those loadings in Equation 10.8 to obtain the PVE.
These two approaches should give the same results.
Hint: You will only obtain the same results in (a) and (b) if the same
data is used in both cases. For instance, if in (a) you performed
prcomp() using centered and scaled variables, then you must center
and scale the variables before applying Equation 10.3 in (b).



10. In this problem, you will generate simulated data, and then perform
PCA and K-means clustering on the data.  
(a) Generate a simulated data set with 20 observations in each of
three classes (i.e. 60 observations total), and 50 variables.
Hint: There are a number of functions in R that you can use to
generate data. One example is the rnorm() function; runif() is
another option. Be sure to add a mean shift to the observations
in each class so that there are three distinct classes.  
(b) Perform PCA on the 60 observations and plot the first two principal
component score vectors. Use a different color to indicate
the observations in each of the three classes. If the three classes
appear separated in this plot, then continue on to part (c). If
not, then return to part (a) and modify the simulation so that
there is greater separation between the three classes. Do not
continue to part (c) until the three classes show at least some
separation in the first two principal component score vectors.  
(c) Perform K-means clustering of the observations with K = 3.
How well do the clusters that you obtained in K-means clustering
compare to the true class labels?  
Hint: You can use the table() function in R to compare the true
class labels to the class labels obtained by clustering. Be careful
how you interpret the results: K-means clustering will arbitrarily
number the clusters, so you cannot simply check whether the true
class labels and clustering labels are the same.
(d) Perform K-means clustering with K = 2. Describe your results.
(e) Now perform K-means clustering with K = 4, and describe your
results.  
(f) Now perform K-means clustering with K = 3 on the first two
principal component score vectors, rather than on the raw data.
That is, perform K-means clustering on the 60 × 2 matrix of
which the first column is the first principal component score
vector, and the second column is the second principal component
score vector. Comment on the results.  
(g) Using the scale() function, perform K-means clustering with
K = 3 on the data after scaling each variable to have standard
deviation one. How do these results compare to those obtained
in (b)? Explain.

